---
title: "Synthetic Data"
subtitle: "Synthea"
page-layout: full
---

This is for creating synthetic data for **Breast Cancer** using [Synthea](<https://github.com/synthetichealth/synthea/wiki>)

`cd synthea`

`./run_synthea -p 1000 -g F -m new_bc --exporter.csv.export=true -- exporter.fhir.export=false --exporter.years_of_history=30`.

**Note**: `exporter.years_of_history` it filters how old will be the data. For instance, if 10 only the newest 10 years will be keep.

`./run_synthea -p 1000 -m BasicModule --exporter.csv.export=true -- exporter.fhir.export=false --exporter.years_of_history=0`.


**Generate Synthetic Patients**

Generating the population one at a time...

```{r eval=FALSE}
./run_synthea
```

Command-line arguments may be provided to specify a state, city, population size, or seed for randomization.

```{r eval=FALSE}
run_synthea [-s seed] [-p populationSize] [state [city]]
```

Full usage info can be printed by passing the `-h` option.  
```{r eval=FALSE}
$ ./run_synthea -h     

> Task :run
Usage: run_synthea [options] [state [city]]
Options: [-s seed]
         [-cs clinicianSeed]
         [-p populationSize]
         [-r referenceDate as YYYYMMDD]
         [-g gender]
         [-a minAge-maxAge]
         [-o overflowPopulation]
         [-c localConfigFilePath]
         [-d localModulesDirPath]
         [-i initialPopulationSnapshotPath]
         [-u updatedPopulationSnapshotPath]
         [-t updateTimePeriodInDays]
         [-f fixedRecordPath]
         [-k keepMatchingPatientsPath]
         [--config*=value]
          * any setting from src/main/resources/synthea.properties

Examples:
run_synthea Massachusetts
run_synthea Alaska Juneau
run_synthea -s 12345
run_synthea -p 1000
run_synthea -s 987 Washington Seattle
run_synthea -s 21 -p 100 Utah "Salt Lake City"
run_synthea -g M -a 60-65
run_synthea -p 10 --exporter.fhir.export=true
run_synthea --exporter.baseDirectory="./output_tx/" Texas
```

### Set age

[Here](https://github.com/synthetichealth/synthea/issues/308) an issue with age

## Demographics

```{r message= FALSE, warning=FALSE}

# Library
library(tidyverse)

# Working directory
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) 
#demographics <- read_csv("synthea/src/main/resources/geography/demographics.csv")

# Get the root directory
#root_dir <- rprojroot::find_rstudio_root_file()

# Remove the "content" directory from the path
#root_dir <- dirname(root_dir)

# Set the root directory
#knitr::opts_knit$set(root.dir = root_dir)


getwd()
#demographics <- read_csv("/Users/igna/Desktop/Synthea/synthea/src/main/resources/geography/demographics.csv")
```